### 2017-01-22 Theory/Theory.tex
More theory

\subsection{The Higgs sector of the MSSM}
\label{sec:theory_MSSM_H}

@@

\section{MSSM benchmark scenarios}
\label{sec:theory_BSM_models}

\subsection{The $m_{h}^{\text{mod+}}$ scenario}
\label{sec:theory_BSM_models_mhmodp}

@@

Gluon fusion dominance? Show decays? Or do it in the relevant subsecs?

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_xsAH.png}
\caption{Cross-sections at $\sqrt{s}=14$ TeV as a function of
\mA~and \tanb~ in 
the hMSSM scenario for b-associated production of \PHiggsps (top left), b-associated
production of \PHiggs (top right), gluon fusion production of \PHiggsps (bottom left) and
gluon fusion production of \PHiggs (bottom right). The white areas indicate cross-sections
smaller than the minimum value on the z-axis. We can generally see the cross-sections increase
with growing \tanb, apart from the gluon fusion cross sections which decrease with increasing
\tanb~for low \tanb~\cite{hMSSM-2}.}
\label{fig:hmssm_xs}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=\textwidth]{./Theory/Figures/hmssm_brtautau.png}
\caption{Branching ratios of \PHiggsps (left) and \PHiggs (right) into \tautau. The
branching ratio is enhanced at high \tanb~\cite{hMSSM-2}.} 
\label{fig:hmssm_brtautau}
\end{figure}

>>>>

\subsection{The Higgs sector of the MSSM}
\label{sec:theory_MSSM_H}
At least two Higgs doublets are required in the
Higgs sector of the MSSM due to the supersymmetric
background of the theory \cite{MSSM-carena-haber}. Two complex Higgs doublets are added,
\begin{equation}\label{eqn:mssm_higgsdoublets}
\phi_d = \begin{pmatrix} \phi_d^0 \\
\phi_d^- \end{pmatrix} \text{ and } \phi_u = \begin{pmatrix} \phi_u^+ \\
\phi_u^0 \end{pmatrix}
\end{equation}
Note that $\phi_d^0$ couples exclusively to down-type fermions, and $\phi_u^0$ couples
exclusively to up-type fermions.
This leads to potential terms in the MSSM Lagrangian of the form:
\begin{equation}\label{eqn:mssm_lagrangian_potential}
V = \mu(\phi_u^+\phi_d^- - \phi_u^0\phi_d^0),
\end{equation}
with $\mu$ a mass parameter, equivalent to the \ac{SM} Higgs mass parameter.
This provides electroweak symmetry breaking as in the \ac{SM} case and
minimising this potential gives,
\begin{equation}\label{eqn:mssm_minimpot}
\langle 0|\phi_d| 0 \rangle = \begin{pmatrix}v_d\\
0 \end{pmatrix} \text{ and} \langle 0 |\phi_d|\rangle 0 = \begin{pmatrix} 0\\
v_u \end{pmatrix}
\end{equation}
Using this we define
\begin{equation}\label{eqn:tanb_def}
\tan{\beta} \equiv \frac{v_u}{v_d}
\end{equation}
Of the eight degrees of freedom due to the introduction of two complex
doublets, three become longitudinal states of the $\PW^{\pm}$ and \PZ bosons.
The remaining 5 degrees of freedom lead to five physical Higgs bosons, a charged
Higgs boson pair $\PHiggs^{\pm}$, the neutral pseudoscalar \PHiggsps
and the neutral scalars h and H. These are defined in terms
of \tanb~and a mixing angle $\alpha$ which arises from diagonalising
the neutral scalar Higgs squared-mass matrix, see equation \ref{eqn:treelevel_mass}. The five bosons become:
\begin{align}\label{eqn:MSSMHiggsMixing}
&\PHiggs^+ = \phi_u^+\cos{\beta} + \phi_d^{-\dagger}\sin{\beta},\\
&\PHiggs^- = \phi_u^{+\dagger}\cos{\beta} + \phi_d^{-}\sin{\beta},\\
&\PHiggsps = \sqrt{2}(\text{Im}\phi_d^0\sin{\beta} + \text{Im}\phi_u^0\cos{\beta}),\\
&\PHiggslight = -(\sqrt{2}\text{Re}\phi_d^0 - v_d)\sin{\alpha} + (\sqrt{s}\text{Re}\phi+u^0 -v_u)\cos{\alpha}\\
&\PHiggs = (\sqrt{2}\text{Re}\phi_d^0-v_d)\cos{\alpha}+(\sqrt{2}\text{Re}\phi_u^0-v_u)\sin{\alpha}
\end{align}
As the self-interactions of the Higgs fields are not independent parameters
but are functions of the electroweak gauge coupling constants, at tree
level the MSSM Higgs sector parameters are determined by two free parameters, \tanb~and
one of the Higgs boson masses, conventionally chosen as \mA.
Using this the masses of the five Higgs states are found as:
\begin{equation}\label{mssm_chargedhigss_mass}
m_{\PHiggs^{\pm}}^2 = m_{\PHiggsps}^2+m_{\PW}^2,
\end{equation}
while the neutral scalar \PHiggslight and \PHiggs are eigenstates of the tree-level
squared-mass matrix:
\begin{equation}\label{eqn:treelevel_mass}
\mathcal{M}_{\text{tree}}^2 = \begin{pmatrix} 
m_{A}^2\sin{\beta}^2 + m_{Z}^2\cos{\beta}^2 & -(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta}\\
-(m_{A}^2+m_{Z}^2)\sin{\beta}\cos{\beta} & m_{A}^2\cos{\beta}^2+m_{Z}^2\sin{\beta}^2 \end{pmatrix}.
\end{equation}
This leads to the masses of \PHiggslight and \PHiggs as eigenvalue of $\mathcal{M}_{\text{tree}}^2$,
\begin{equation}\label{eqn:scalarmass}
m_{\PHiggs,\PHiggslight}^2 = \frac{1}{2}(m_{A}^2+m_{Z}^2 \pm \sqrt{(m_A^2+m_Z^2)^2-4m_Z^2m_A^2\cos{2\beta}^2}).
\end{equation}
A consequence of this is a tree-level upper bound to the mass of the light Higgs
boson,
\begin{equation}\label{eqn:mh_upper}
m_{h} \leq m_{Z},
\end{equation}
and a constraing on $\alpha$,
\begin{equation}\label{eqn:alpha_constraint}
\cos{(\beta-\alpha)}^2 = \frac{m_h^2(m_Z^2-m_h^2)}{m_A^2(m_H^2-m_h^2)}.
\end{equation}

The constraint on $m_h$ being less than the mass of the Z boson, 91.2 GeV, seems 
problematic at first, as we know there is a Higgs state with a mass of 125 GeV. However,
the tree-level masses and couplings of the Higgs bosons in the MSSM can be
significantly altered by radiative corrections. The dominat effect is from
incomplete cancellation of the stop- and top-loop corrections, which
do not completely cancel as SUSY is a broken symmetry. FIND REFERENCE FOR THIS

The couplings of the neutral Higgs bosons to bosons and fermions 
are modified with respect to the \ac{SM} couplings, by factors
described in table \ref{tab:mssm_couplings} \cite{YR4}.

\begin{table}[htp]
\label{tab:mssm_couplings}
\begin{center}
\caption{Couplings in the MSSM, as multiplicative factors with
respect to the \ac{SM} couplings}
\begin{tabular}{p{2cm}p{4cm}p{4cm}p{4cm}}
\toprule
Particle & Coupling to bosons & Coupling to up-type quarks & Coupling to down-type quarks and leptons \\
\midrule
\PHiggsps & 0 & $\cot{\beta}$ & $ \tan{\beta}$\\
\PHiggs & $\cos{\beta-\alpha}$ & $\frac{\sin{\alpha}}{\sin{\beta}}$ & $\frac{\cos{\alpha}}{\cos{\beta}}$\\
\PHiggslight & $\sin{\beta-\alpha}$ & $\frac{\cos{\alpha}}{\sin{\beta}}$ & $-\frac{\sin{\alpha}}{\cos{\beta}}$\\
\bottomrule
\end{tabular}
\label{tab:mssm_couplings}
\end{center}
\end{table}

In the \textit{decoupling limit}, when \mA$>>m_{Z}$, the mixing
angle $\alpha \approx \beta - \pi/2$. This reduces the couplings in table
\ref{tab:mssm_couplings} to the \ac{SM} couplings for the \PHiggslight boson, 
with negligible couplings to bosons for the two remaining neutral
Higgs bosons, couplings to down-type quarks and leptons enhanced by a factor \tanb,
and couplings to up-type quarks enhanced by a factor $\frac{1}{\tan{\beta}}$.
%Using trigon identities: cos alpha/cos beta = cos (beta-pi/2)/cos beta = cosbeta*cospi/2 + sin(beta)*sin(pi/2) over cos beta = sin beta /cos beta = tan beta
%sin alpha = sin (beta-pi/2) = sinbeta cos pi/2 - cosbetasinpi/2 = -cosbeta 
%such that -sinalpha/cosbeta = 1
%cos alpha/sin beta = sin beta/sin beta = 1
%sin beta-alpha = sin pi/2 = 1
%cos beta-alpha = cos pi/2 = 0
%sin alpha/sin beta = -cos beta/sin beta=-1/tan(beta)

@@

\section{MSSM benchmark scenarios}
\label{sec:theory_BSM_models}
Because the MSSM contains a large number of
SUSY-breaking parameters that affect the Higgs
sector, it us usual to define benchmark scenarios 
in which the only free parameters are \mA~and \tanb.
In these scenarios the SUSY parameters entering in 
the radiative corrections are fixed to define the scenario.

The parameters that need to be fixed in the benchmark scenarios are:
\begin{itemize}
\item The mass of the third generation squarks, given by $M_{\text{SUSY}}$.
\item The higgsino mass parameter, $\mu$.
\item The mass of the stau, the third generation sleptons, $M_{\tilde{\ell_3}}$.
\item The mass of the gluino, $M_{\tilde{g}}$.
\item The U(1) gaugino mass parameter, $M_1$.
\item The SU(2) gaugino mass parameter, $M_2$.
\item The trilinear couplings of the stops, sbottoms and staus to the Higgs: $A_t$, $A_b$ and $A_{\Pgt}$.
\item The stop, sbottom and stau mixing parameters, $X_t$, $X_b$ and $X_{\Pgt}$.
\end{itemize}

Some of these parameters can be expressed in terms of relations to other parameters. 
$X_t$, $X_b$ and $X_{\Pgt}$ can be expressed as,
\begin{equation}\label{eqn:trilinear_couplings}
\begin{split}
&X_t = A_t-\mu\cot{\beta},\\
&X_b = A_b-\mu\tan{\beta},\\
&X_{\Pgt} = A_{\Pgt} - \mu\tan{\beta}.
\end{split}
\end{equation}
In addition, $M_1$ is fixed via the unification
relation,
\begin{equation}
M_1 = \frac{5}{3}M_s\tan{\theta_w}^2,
\end{equation}
where $\theta_w$ is defined by $\cos{\theta_w} = \frac{m_W}{m_Z}$.

Some additional parameters which have only a
small effect on the MSSM Higgs boson sector are alos considered.
Because their effect is so small they are
fixed in all benchmark scenarios at values compatible with 
exclusion limits from direct searches:
\begin{itemize}
\item Masses of the first and second generation squarks, $M_{\tilde{q}_{1,2}} = 1.5$ TeV.
\item Masses of the first and second generation sleptons, $M_{\tilde{\ell}_{1,2}} = 500$ GeV.
\item Trilinear couplings of first and second generation squarks and sleptons, $A_f=0$.
\end{itemize}

After the discovery of the 125 GeV Higgs boson the MSSM benchmark
scenarios need to accommodate this particle, which means only the 
scenarios which contain a light Higgs boson with a mass of around 125 GeV
are still accessible.

% in the mmax scenario the benchmark values have been chosen h
%such that the mass of the light CP-even Higgs boson is maximized for fixed tanβ and large
%MA (the scale of the soft SUSY-breaking masses in the stop and sbottom sectors, which
%sets the mass scale for the corresponding supersymmetric particles, has been fixed to 1 TeV
%in this scenario). This scenario is useful to obtain conservative bounds on tanβ for fixed
%values of the top-quark mass

\subsection{The $m_{h}^{\text{mod+}}$ scenario}
\label{sec:theory_BSM_models_mhmodp}
The $m_{h}^{\text{mod+}}$ scenario \cite{MSSM-benchmark-scenarios}
is a modification of the $m_h^{\text{max}}$ scenario \cite{MSSM-mhmax}. This scenario, which
was used for interpretations of MSSM Higgs boson searches at LEP, allows
the mass of the light Higgs boson to reach the highest a-priori expected 
value of around 135 GeV for high \mA. There is only a small area of the \mA-\tanb~plane
in this scenario where the mass of the light Higgs boson is compatible with the
observed 125 GeV state. The modifications to the parameters of the $m_{h}^{\text{max}}$ 
scenario address this issue. In the $m_{h}^{\text{mod+}}$ scenario $M_{\text{SUSY}}$ is chosen
to be 1 TeV. The stop mixing parameter is positive, $X_t= 1.5 M_{\text{SUSY}}$.
%This gives better agreement with muon g-2 results while the mhmod- scenario
%negative stop mixing (-1.9 M_SUSY) results in better agreements with B(b->sgamma) 
%meausrements 
The remaining parameters are set as $\mu=200$ GeV, $m_{\tilde{g}} = 1.5$ TeV,
$m_{\tilde{\ell}_3} = 1$ TeV, and $A_b=A_t=A_{\Pgt}$. Figure \ref{fig:mhmodp_mh}
shows the mass of the light Higgs boson in the $m_{h}^{\text{mod+}}$ scenario, showing
that its mass is compatible with 125 GeV over a large part of the parameter space.
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./Theory/Figures/mh_mhmodp.pdf}
\end{center}
\caption{The mass of the light Higgs boson, \mh, as a function 
of \mA~and \tanb~in the $m_{h}^{\text{mod+}}$ scenario. The white areas
indicate masses lower than 122 GeV. The figure shows that
the mass of the light Higgs boson is compatible with 125 GeV over a large
part of the \mA-\tanb~plane.}
\label{fig:mhmodp_mh}
\end{figure}

Figure \ref{fig:mhmodp_xs} shows the cross--sections of
gluon fusion production of the \PHiggs boson and (four--flavour scheme) b-associated
production of the \PHiggsps boson in the $m_h^{\text{mod+}}$ scenario. Gluon fusion 
production dominates at low \tanb, while b-associated production has a larger cross--section
at high \tanb.

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma(gg\rightarrow \PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_ggH_mhmodp.pdf}}
\subfloat[$\sigma(gg\rightarrow bb\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xs_bbA4FS_mhmodp.pdf}}
\end{center}
\caption{Production cross--section of (a) gluon fusion production of the \PHiggs boson and
(b) b--associated production (four--flavour scheme) of the \PHiggsps boson in the $m_{h}^{\text{mod+}}$ scenario. The gluon fusion production cross section is larger at low \tanb, while
the b-associated production cross-section is larger at high \tanb.}
\label{fig:mhmodp_xs}
\end{figure}

Figure \ref{fig:mhmodp_br} shows the branching ratio of the \PHiggs and \PHiggsps 
into $\tau\tau$. The branching ratios into $\tau\tau$ are enhanced, especially at
high \tanb, showing how this decay channel is useful for MSSM Higgs boson searches.

\begin{figure}[h!]
\begin{center}
\subfloat[BR($\PHiggs \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_mhmodp.pdf}}
\subfloat[BR($\PHiggsps \rightarrow \tau\tau$)]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_mhmodp.pdf}}
\end{center}
\caption{Branching ratio of (a) \PHiggs and (b) \PHiggsps into $\tau\tau$. The branching
ratios into $\tau\tau$ are enhanced at high \tanb.}
\label{fig:mhmodp_br}
\end{figure}

@@

@@

\begin{figure}[h!]
\begin{center}
\subfloat[$\sigma(gg\rightarrow\PHiggsps)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsggA_hmssm.pdf}}
\subfloat[$\sigma(bb\rightarrow bb\PHiggs)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/xsbbH4F_hmssm.pdf}}
\end{center}
\caption{Cross-sections at $\sqrt{s}=13$ TeV as a function of
\mA~and \tanb~ in 
the hMSSM scenario for (a) gluon fusion production of the \PHiggsps boson and (b)
b-associated production (four--flavour scheme) of the \PHiggs boson. We can generally see the cross-sections increase
with growing \tanb, apart from the gluon fusion cross section which decrease with increasing
\tanb~for low \tanb.}
\label{fig:hmssm_xs}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\subfloat[BR$(\PHiggs\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brHtautau_hmssm.pdf}}
\subfloat[BR$(\PHiggsps\rightarrow\Pgt\Pgt)$]{\includegraphics[width=0.5\textwidth]{./Theory/Figures/brAtautau_hmssm.pdf}}
\end{center}
\caption{Branching ratios of (a) the \PHiggs boson and (b) the \PHiggsps boson into \tautau. The
branching ratio is enhanced at high \tanb.} 
\label{fig:hmssm_brtautau}
\end{figure}
